---
title: "Exercise #06"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Clemens (redacted for github), Mark (redacted for github), Joseph (redacted for github)
date: "`r Sys.Date()`"
output: distill::distill_article
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.
-   Make sure to submit you render your Rmarkdown as
    `distill:distill_article` and check the final output regarding any
    issues in formatting. Formatting errors may lead to point
    deductions.

## Exercise 1: Building an R package (20 Points)

For this exercise we ask you to build an R package. We do not ask you to
build any particular R package, but leave the choice of what your R
package will do up to you, to keep it more interesting for you.

Instead of having particular tasks for you to complete, we have a list
of requirements for your final R package and submission. Please submit
an Rmd and render it as always, although you will only have to provide
the short information asked for under *Submission*.

We advise you to start early with this exercise sheet and encourage you
to reach out if you encounter issues during the creation of your
package. For detailed information on all aspects of creating an R
package, we highlight again, the [great book on R
packages](https://r-pkgs.org/) by Hadley Wickham.

We look forward to seeing the cool packages you come up with and thank
you for participating in the course!

### Functionality

a)  Create a working R package that performs the task it is intended to
    
b)  Your R package needs to be installable (test this before submitting)

c)  Your R package should contain at least 2 functions

d)  The functions in your R package should be properly documented
    according to the Roxygen convention. Each function should include an
    `@example` tag.

e)  The documentation for your package should be properly generated and
    up-to-date. After every change to the Roxygen comments of your
    functions, you will need to run `devtools::document()` again to do
    this.

f)  The `DESCRIPTION` file of your package should be properly formatted
    and contain all the required dependencies of your package. It should
    also provide an accurate `Title` and `Description` for your package.


### Submission

a) Briefly describe in one - two sentences what your R package does and
   why you decided to choose this functionality. This is just intended
   to give us some context to better understand the package.
   
   To aid our current studies in Machine learning we decided to create an interactive tool for visualizing how a random forest grows and gets better with each added Tree.  
   We wanted to create an easy way to explore performance of random-forest ML-models on a multitude of different data sets, while playing around with test sets and model parameters, while potentially even unlocking multithreaded performance of our computers.

b) To make installation easier, your R package should be in a public
   repository on GitHub. Provide the URL to the GitHub repository
   below:

   e.g. `https://github.com/<YOUR_GH_USERNAME>/<PACKAGE_REPOSITORY_NAME>`

c) Your R package should be installable via
   `remotes::install_github()`. Before submitting your solution to this
   exercise sheet please test whether you can install your R package
   from GitHub. Provide the command below:

    ``` {r}
    remotes::install_github("<YOUR_GH_USERNAME>/<PACKAGE_REPOSITORY_NAME>")
    ```

### Useful for the Authors

    ```{r, install required packages}
    # 0) In a clean R session ----
    # install.packages(c("devtools", "roxygen2", "randomForest", "ggplot2",
    #                   "dplyr", "tibble", "magrittr"))
    ```
    
    ```{r, rebuild package from scratch}
    # 1) Create the skeleton in a new folder
    
    setwd("/home/clemi/Documents/Uni/Info/4Semester/statsoft2/gradedExercises/06/forestSim/")
    unloadNamespace("forestSim")
    
    # 2) Drop the files shown above into that folder
    #    (or copy‑paste them in RStudio's file explorer)
    
    # 3) Document & install
    
    # devtools::document("../forestSim")
    # devtools::install("../forestSim")
    
    # 4) Quick smoke test
    
    # library(forestSim)                   # load newly created package
    sim <- simulate_forest(iris, target = "Species", ntree = 50)
    head(sim)
    plot_accuracy_growth(sim)            # should open a line plot
    
    ```


    ```{r, dry run}
    # 1) Quick smoke test
    library(forestSim)                   # load newly created package
    sim <- simulate_forest(
     data = ChickWeight, 
     target = "weight", 
     ntree = 150,
     mtry = 2,
     test_fraction = 0.3,
     test_frac_seed = 42
    )
    plot_accuracy_growth(sim)
    
    # 2) Quick smoke test2
    sim2 <- simulate_forest_multi(
      data = head(ggplot2::diamonds, n = 1000),
      n_runs = 4,
      target = "cut",
      ntree = 100,
      mtry = 2,
      test_fraction = 0.5,
      )
    plot_accuracy_growth_multi(sim2)    
    ```
